Kindly Bent to Free Us

### 2020-03-04 kindly/motivation-pool.tex
fixed syntax rewriting

\begin{lstlisting}
(* Using the pool in queries. *)
let create_user pool name =
  Pool.use &pool (fun connection ->
    Db.insert "users" [("name", name)] connection)

let uri = "postgresql://localhost:5432"
let main users =
  (* Create a database connection pool. *)
  let pool = Pool.create (fun _ -> Db.connect uri) in
  List.parallel_iter (create_user &pool) users;
  Pool.consume (fun c -> Db.close c)
\end{lstlisting}
    \vspace{-8pt}
    \caption{Example of use}
    \label{ex:pool}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\linewidth}
\begin{lstlisting}
type ('a:'k) pool : 'k =
  { spawn: unit -> 'a; queue: 'a CQueue.t }
let create spawn = 
  { spawn ; queue = CQueue.create () }
let consume f c = CQueue.iter f c.queue
let use { spawn ; queue } f =
  let o = match CQueue.pop &queue with
    | Some x -> x
    | None () -> spawn ()
  in
  let r = {| f &!o |} in(*@\label{line:pool:region}*)
  CQueue.push o &queue;
  r
\end{lstlisting}
    \vspace{-8pt}
    \caption{Implementation}
    \label{impl:pool}
  \end{subfigure}

>>>>

\begin{lstlisting}
(*Using the pool in queries.*)
let create_user pool name =
  Pool.use &pool (fun connection ->
    Db.insert "users" [("name", name)] connection)

let uri = "postgresql://localhost:5432"
let main users =
  (*Create a database connection pool.*)
  let pool = Pool.create (fun _ -> Db.connect uri) in
  List.parallel_iter (create_user &pool) users;
  Pool.consume (fun c -> Db.close c)
\end{lstlisting}
    \vspace{-8pt}
    \caption{Example of use}
    \label{ex:pool}
  \end{subfigure}
  \hfill
  \begin{subfigure}[t]{0.45\linewidth}
\begin{lstlisting}
type ('a:'k) pool : 'k =
  { spawn: unit -> 'a; queue: 'a CQueue.t }
let create spawn = 
  { spawn ; queue = CQueue.create () }
let consume f c = CQueue.iter f c.queue
let use { spawn ; queue } f =
  let o = match CQueue.pop &queue with
    | Some x -> x
    | None () -> spawn ()
  in
  let r = {| f &!o |} in(*@\label{line:pool:region}*)
  CQueue.push o &queue;
  r
\end{lstlisting}
    \vspace{-8pt}
    \caption{Implementation}
    \label{impl:pool}
  \end{subfigure}
